cooking

### 2019-11-15 inst/cook.Rmd
more work on the loser

>>>>

# Just the loser

Now we are going to look at what happens when our observation is only
the _loser_ (which is me).  We have two hypotheses

* $H_1: \mbox{I might very well be the worst chef in the family}$
* $H_2: \mbox{I am not the worst chef in the family}$

Observe that $H_2$ implies that someone is worse than me and this
corresponds to a restricted parameter space.  The first step is to
define a suitable likelihood function for our observation:

```{r}
n <- 6 # number of people in the family
H <- hyper2(pnames=letters[1:6])
L <- ggol(H,letters[2:n],letters[1])
L[[1]]
L[[2]]
```

In the above, `L` is a list of hyper2 objects corresponding to a
possible order statistic (we see the first two).  Any order is
permissible, so long as player `a` (me) is bottom.  Now we maximize
the likelihood under $H_1$, that is, perform an unconstrained
maximization:

```{r}
(ans_unconstrained <- maxplist(L,give=TRUE))
```

The likelihood at the evaluate is 1 (technically, this is wrong
because likelihood is defined only up to a multiplicative constant.  A
correct statement is: the likelihood function evaluated by
`like_single_list()` returns 1).  The next step is to perform a
constrained maximization, the constraint being that I am better than
at least one other person, here chosen to be person `b`:

```{r}
small <- 1e-2  # numerical necessity
ans_constrained <-
maxplist(L,startp=c(small*2,rep(small,n-2)),fcm=rbind(c(1,-1,rep(0,n-3))),fcv=0,give=TRUE)
ans_constrained
```

We can see that the likelihood ratio ${\mathcal L}(H_2)/{\mathcal
L}(H_1)$ is 0.5 for an observation that I come last.  This is exactly
the same as the likelihood ratio for the following situation: we toss
a coin which is either fair ($H_\mbox{fair}$) or two-headed
($H_\mbox{2heads}$).  We observe a head.  Then ${\mathcal
L}(H_\mbox{2heads})/{\mathcal L}(H_\mbox{fair}) = 0.5$ as well (this
is Edwards's valet and black and white ball thought experiment).
